TBD

### 2016-10-13 paper.tex
more progress on CG section

\section{Conjugate Gradient Method}
The Conjugate Gradient (CG) method was independently discovered by \citet{Hestenes1973} and \citet{Stiefel1952}. They later published a joint paper, which is now considered as the seminal
reference on CG \citep{Hestenes1952}. The iterative CG method is used to solve a particular class of linear systems. The CG method is generally used to solve
\begin{equation}
\label{eq:linear_system}
\bb = \bA\bx,
\end{equation}
where $\bb\in\mathbb{C}^P$ is a known complex column vector of size $P$, $\bx\in\mathbb{C}^P$ is an unknown complex column vector with the same length as $\bb$, and $\bA\in\mathbb{C}^{P\times P}$ is a square positive-definite Hermitian matrix with the appropriate dimensions.  
Moreover, using the CG method to solve Eq.~\eqref{eq:linear_system} will only be computationally advantageous if $\bA$ is also sparse (contain many zero entries).
Using the iterative CG method to solve large sparse linear sytems was popularized by \citet{Reid1971}. A good tutorial on the CG method can be found in \citep{Shewchuk1994}.

@@

\begin{algorithm}
\caption{Conjugate Gradient Method}\label{algo:CG}
\begin{algorithmic}[1]
\State $\br \gets \bA\bx_0 - \bb$
\State $\bp \gets -\br_0$
\For{$k\leq k_{\textrm{max}}$}
\State $\alpha_k \gets \frac{\br_k^H\br_k}{\bp_k^H\bA\bp_k}$
\State $\bx_{k+1} \gets \bx_k + \alpha_k\bp_k$
\State $\br_{k+1} \gets \br_k - \alpha_k\bA\bp_k$
\If{$\|\br_{k+1}\|<\epsilon\|\br_0\|$}
\State break
\EndIf
\State $\beta_{k} \gets \frac{\br_{k+1}^H\br_{k+1}}{\br_k^H\br_k}$
\State $\bp_{k+1} \gets \br_{k+1} + \beta_{k}\bp_k$
\State $k \gets k + 1$
\EndFor
\end{algorithmic}
\end{algorithm}

\subsection{Computational Complexity}
\citet{Kaniel1966} was able to determine convergence bounds for CG using Chebyshev polynomials. A much more in depth analysis of CG convergence can be found in
\citep{Sluis1986}.
The computational complexity of CG is $\mathbb{O}(\sqrt{\kappa}m)$, where $\kappa$ is the generalized specctral condition number of the matrix $\bA$ and $m$ is the number of
non-zero entries in the matrix $\bA$. The mathematical
definition of $\kappa(\bA)$ is
\begin{equation}
\kappa(\bA) = \frac{\lambda_{\textrm{max}}}{\lambda^{+}_{\textrm{min}}}, 
\end{equation}
where $\lambda_{\textrm{max}}$ denotes the largest eigenvalue of $\bA$ and $\lambda^{+}_{\textrm{min}}$ presents the smallest positive eigenvalue. 
Interpreting the computational complexity equation further. Note from Algorithm 1 that the CG method has one major outer loop. In the worst possible case, the amount of iterations needed to converge is
proportional to $\sqrt{\kappa}$. Also notice that the most expensive 
operation that is conducted within each loop is the vector-matrix product, which has complexity $\mathbb{O}(m)$, where $m$ is the number of non-zero entries in the matrix.
The computational complexity of the CG method is therefore 
\begin{equation}
\mathbb{O}(\sqrt{\kappa}m) 
\end{equation}

>>>>

\section{Conjugate Gradient Method}
The Conjugate Gradient (CG) method was independently discovered by \citet{Hestenes1973} and \citet{Stiefel1952}. They later published a joint paper, which is now considered as the seminal
reference on CG \citep{Hestenes1952}. The iterative CG method is used to solve a particular class of linear system. The CG method is generally used to solve
\begin{equation}
\label{eq:linear_system}
\bb = \bA\bx,
\end{equation}
where $\bb\in\mathbb{C}^P$ is a known complex column vector of size $P$, $\bx\in\mathbb{C}^P$ is an unknown complex column vector with the same length as $\bb$, and $\bA\in\mathbb{C}^{P\times P}$ is a square positive-definite Hermitian matrix with the appropriate dimensions.  
Moreover, using the CG method to solve Eq.~\eqref{eq:linear_system} will only be computationally advantageous if $\bA$ is also sparse (contain many zero entries).
Using the iterative CG method to solve large sparse linear sytems was popularized by \citet{Reid1971}. A good tutorial on the CG method can be found in \citep{Shewchuk1994}.
The iterative CG method is presented in Algorithm \ref{algo:CG}.

@@

\begin{algorithm}
\caption{Conjugate Gradient Method. Inputs: $\bA$, $\bb$, a starting value $x$, maximum number of iterations $k_{\textrm{max}}$ and an error tolerance $\epsilon<1$ Output: $\bx$ the solution to Eq.~\eqref{eq:linear_system}. \citep{Shewchuk1994}.}\label{algo:CG}
\begin{algorithmic}[1]
\State $k \gets 0$
\State $\br \gets \bb - \bA\bx$
\State $\bp \gets \br$
\State $\delta_{\textrm{new}} \gets \br^H\br$
\State $\delta_0 \gets \delta_{\textrm{new}}$
\While{$k\leq k_{\textrm{max}}$ and $\delta_{\textrm{new}} > \epsilon^2\delta_0$}
\State $\alpha_k \gets \frac{\delta_{\textrm{new}}}{\bp^H\bA\bp}$
\State $\bx \gets \bx + \alpha_k\bp$
\State $\br \gets \br - \alpha\bA\bp$
\State $\delta_{\textrm{old}} \gets \delta_{\textrm{new}}$ 
\State $\delta_{\textrm{new}} \gets \br^H\br$
\State $\beta_{k} \gets \frac{\delta_{\textrm{new}}}{\delta_{\textrm{old}}}$
\State $\bp \gets \br + \beta\bp$
\State $k \gets k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

\subsection{Computational Complexity}
\citet{Kaniel1966} was able to determine convergence bounds for CG using Chebyshev polynomials. A much more in depth analysis of CG convergence can be found in
\citep{Sluis1986}. As can be seen from Algorithm \ref{algo:CG}, the CG method makes use of only one major outer loop. It turns out that in the worst possible case 
the number of major iterations that is required by CG to converge is proportional to $\sqrt{\kappa}$.

The computational complexity of CG is $\mathbb{O}(\sqrt{\kappa}m)$, where $\kappa$ is the generalized specctral condition number of the matrix $\bA$ and $m$ is the number of
non-zero entries in the matrix $\bA$. The mathematical
definition of $\kappa(\bA)$ is
\begin{equation}
\kappa(\bA) = \frac{\lambda_{\textrm{max}}}{\lambda^{+}_{\textrm{min}}}, 
\end{equation}
where $\lambda_{\textrm{max}}$ denotes the largest eigenvalue of $\bA$ and $\lambda^{+}_{\textrm{min}}$ presents the smallest positive eigenvalue. 
Interpreting the computational complexity equation further. Note from Algorithm 1 that the CG method has one major outer loop. In the worst possible case, the amount of iterations needed to converge is
proportional to $\sqrt{\kappa}$. Also notice that the most expensive 
operation that is conducted within each loop is the vector-matrix product, which has complexity $\mathbb{O}(m)$, where $m$ is the number of non-zero entries in the matrix.
The computational complexity of the CG method is therefore 
\begin{equation}
\mathbb{O}(\sqrt{\kappa}m) 
\end{equation}
